\Title

### 2023-07-12 Grimaldi-etal-BiolCybernetics.tex
Update Grimaldi-etal-BiolCybernetics.tex

If we now widen our focus on the interpretation of these kernels in terms of spatiotemporal motifs embedded in the event stream, these show a prototypical anisotropic profile adapted to motion detection~\citep{kaplan_anisotropic_2013}. In~\citep{grimaldi_robust_2022}, a link was drawn between event-based MLR training and Hebbian learning, allowing to say that the present model learns its weights according to a presynaptic activity associated to the different motion directions. Each neuron becomes selective to a specific motion direction through the learning of an associated prototypical spatiotemporal spiking motif. Each voxel in the 3D kernels defines a specific property by associating a weight to a position and a delay. Consequently, our model is able to detect precise spatiotemporal motifs embedded in the spike train and associated to the different motion directions. Note that as the delays become larger, two effects can be remarked. First, coefficients become lower which is consistent with the fact that trajectories are defined in a piece wise fashion, such that this decrease provides with an optimal integration considering the gradual diminishing of evidence as time progresses~\citep{Pasturel2020}. Second, coefficients become less localized compared to the kernel's spatial profile at short delays, consistent with the average diffusion of information included in the generative model and with the diffusion introduced in motion-based prediction models~\citep{perrinet_motion-based_2012,khoei_flash-lag_2017}. %This conic shape along the motion's trajectory highlights a loss of precision for longer delays, i.e. events away in the past.
%
%
\subsection{Accuracy versus efficiency trade-off}% for the motion detection task}
%%%-----------------------------------------------------------------
%
%%%-----------------------------------------------------------------
%: fig:accuracy
%%%-----------------------------------------------------------------
\begin{figure}%[h!]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/conv_HD-SNN.pdf}
    \caption{
        In response to an instance of the event-based input (Left), we show the neural activity of the HD-SNN model (Right). For visualization purposes, we show only one spatio-temporal slice for a given vertical position ($y = 32$), for a quarter of horizontal positions. The input spiking activity consists of ON and OFF spikes (as in~\seeFig{motion_task}) and illustrates the switching of the naturalistic event-based stream from one motion to another. The output activity consists of an analog component corresponding to the evidence accumulated by the model on the spatio-temporal kernels, and a spiking part (overlaid on this activity as vertical bars) which corresponds to instants when this evidence is above the spiking threshold. Note that this activity is consistent with the motion of the input stream. The class of each output neuron is represented by a similar color as in \seeFig{motion_task}. Finally, an accuracy can be computed by comparing the ground truth motion in the input movie with that predicted by the model.
        }
    \label{fig:activity}
\end{figure}
%
After training our MLR model, we obtain spatiotemporal kernels corresponding to the weights associated with the heterogeneous delays of our layer of spiking neurons, which can be used for detection. For this, we quantify its ability to categorize different motions, i.e. on event streams for which the ground truth motion is known at each instant. The accuracy was computed on a novel dataset of $200$ novel movies. The accuracy computed on the test set was approximately $91\%$ (with a chance level of $1 / 12/ 3 \approx 2\%$). %Moreover, we observed that the classification performance obtained for the model using time surfaces as in~\citep{grimaldi_robust_2022} gives similar results as our method.

>>>>

If we now widen our focus on the interpretation of these kernels in terms of spatiotemporal motifs embedded in the event stream, these show a prototypical anisotropic profile adapted to motion detection~\citep{kaplan_anisotropic_2013}. In~\citep{grimaldi_robust_2022}, a link was drawn between event-based MLR training and Hebbian learning, allowing to say that the present model learns its weights according to a presynaptic activity associated to the different motion directions. Each neuron becomes selective to a specific motion direction through the learning of an associated prototypical spatiotemporal spiking motif. Each voxel in the 3D kernels defines a specific property by associating a weight to a position and a delay. Consequently, our model is able to detect precise spatiotemporal motifs embedded in the spike train and associated to the different motion directions. Note that as the delays become larger, two effects can be remarked. First, coefficients become lower which is consistent with the fact that trajectories are defined in a piece wise fashion, such that this decrease provides with an optimal integration considering the gradual diminishing of evidence as time progresses~\citep{Pasturel2020}. Second, coefficients become less localized compared to the kernel's spatial profile at short delays, consistent with the average diffusion of information included in the generative model and with the diffusion introduced in motion-based prediction models~\citep{perrinet_motion-based_2012,khoei_flash-lag_2017}. %This conic shape along the motion's trajectory highlights a loss of precision for longer delays, i.e. events away in the past.
\subsection{Accuracy versus efficiency trade-off}% for the motion detection task}
%: fig:accuracy
    \includegraphics[width=0.95\linewidth]{figures/conv_HD-SNN.pdf}
        In response to an instance of the event-based input (Left), we show the neural activity of the HD-SNN model (Right). For visualization purposes, we show only one spatio-temporal slice for a given vertical position ($y = 32$), for a quarter of horizontal positions. The input spiking activity consists of ON and OFF spikes (as in~\seeFig{motion_task}) and illustrates the switching of the naturalistic event-based stream from one motion to another. The output activity consists of an analog component corresponding to the evidence accumulated by the model on the spatio-temporal kernels, and a spiking part (overlaid on this activity as vertical bars) which corresponds to instants when this evidence is above the spiking threshold. Note that this activity is consistent with the motion of the input stream. The class of each output neuron is represented by a similar color as in \seeFig{motion_task}. Finally, an accuracy can be computed by comparing the ground truth motion in the input movie with that predicted by the model.
    \label{fig:activity}
After training our MLR model, we obtain spatiotemporal kernels corresponding to the weights associated with the heterogeneous delays of our layer of spiking neurons, which can be used for detection. For this, we quantify its ability to categorize different motions, i.e. on event streams for which the ground truth motion is known at each instant. When applied to new instances of the input movies, the model develops a neural activity which may be used to infer the correct motion~\seeFig{activity} and from which we may deduce an accuracy value. This accuracy was computed on a novel dataset of $200$ novel movies. The accuracy computed on the test set was approximately $91\%$ (with a chance level of $1 / 12/ 3 \approx 2\%$). %Moreover, we observed that the classification performance obtained for the model using time surfaces as in~\citep{grimaldi_robust_2022} gives similar results as our method.
